---
title: Tag label
editor: source
description: https://raphaelnussbaumer.com/GeoPressureManual/geopressuretemplate-label.html
---

This script will guide you through the tag labeling of pressure and/or acceleration data and creation of the pressure map.

```{r setup, message=FALSE}

# Choose the id
id <- "34KB"

# Set the directory to the project root
# see Working directory bullet point in https://bookdown.org/yihui/rmarkdown/notebook.html#executing-code
knitr::opts_knit$set(root.dir = here::here())
# Alternatively, you can change the global RStudio settings in menu "Tools/Global Options...", on the "R Markdown" panel, choose "Project" for "Evaluate chunks in directory:"

# Development version:
# pak::pkg_install("GeoPressure/GeoPressureR@dev")
# pak::pkg_install("GeoPressure/GeoPressureR")
# packageVersion("GeoPressureR")
# remove.packages("GeoPressureR")

library(GeoPressureR)
library(ggplot2)
library(plotly)
```

## Edit `config.yml`

Check that the config is correct.

```{r}
geopressuretemplate_config(id)
```

## Sensor data and crop date

Check if the crop dates (in red) are correct.

```{r crop_date}
ggplotly(
  tag_create(id, quiet = TRUE) |>
    plot(type = "pressure", plot_plotly = FALSE) +
    geom_vline(
      xintercept = c(
        as.POSIXct(config::get("tag_create", id)$crop_start),
        as.POSIXct(config::get("tag_create", id)$crop_end)
      ),
      color = "red",
      lwd = 1
    )
)
```

You might want to change `type` to check the values of the other sensors (e.g., `acceleration` or `light`).

Create tag with cropped date:

```{r tag_create}
tag <- tag_create(
  id,
  crop_start = config::get("tag_create", id)$crop_start,
  crop_end = config::get("tag_create", id)$crop_end
)
```

## Labeling

Use the trainset shiny app for labeling

```{r}
#| eval: false
trainset(tag)
```



```{r}
#| eval: false
tag <- tag_create(
  id,
  crop_start = config::get("tag_create", id)$crop_start,
  crop_end = config::get("tag_create", id)$crop_end
) |>
  tag_label() |>
  tag_set_map(
    extent = config::get("tag_set_map", id)$extent,
    scale = 5, # Use a coarse scale at first 1° is usually enough
    known = config::get("tag_set_map", id)$known
  ) |>
  geopressure_map(workers = 1) 
```

Run GeoPressureViz:

```{r}
#| eval: false
geopressureviz(tag, path = tag2path(tag, interp = 1))
```
