---
title: Twilight label
editor: source
description: https://raphaelnussbaumer.com/GeoPressureManual/geopressuretemplate-twilight.html
---


```{r setup}
id <- "34KB"

knitr::opts_knit$set(root.dir = here::here())
library(GeoPressureR)
library(ggplot2)
```

## Create tag

Make sure you have already created the label file with the "1-label.qmd" script.

```{r}
tag <- tag_create(
  id,
  crop_start = config::get("tag_create", id)$crop_start,
  crop_end = config::get("tag_create", id)$crop_end,
  quiet = TRUE
) |>
  tag_label(quiet = TRUE) |>
  tag_set_map(
    extent = config::get("tag_set_map", id)$extent,
    scale = config::get("tag_set_map", id)$scale,
    known = config::get("tag_set_map", id)$known
  )
```

## Create Twilight

Generate the twilight automatically. Check that `twl_offset` allows for night/day being centered on the figure, otherwise edit accordingly

```{r}
tag <- twilight_create(
  tag,
  twl_offset = config::get("twilight_create", id)$twl_offset
)
plot(tag, type = "twilight")
```

## Annotate twilight in GeoLightViz

```{r}
#| eval: false
geolightviz(tag)
```

## Compute likelihood map

```{r}
tag <- twilight_label_read(tag)
tag <- geolight_map(
  tag,
  twl_calib_adjust = config::get("geolight_map", id)$twl_calib_adjust,
  twl_llp = config::get("geolight_map", id)$twl_llp,
  fitted_location_duration = config::get(
    "geolight_map",
    id
  )$fitted_location_duration
)
```

`twl_calib_adjust`, `fitted_location_duration` and `twl_llp` can generally be left to default, but can be modified in `config.yml` if needed.

## Check

### Check calibration

```{r}
plot_twl_calib(tag)
```

### Check light map

```{r}
plot(tag, type = "map_light")
```

### Check with pressure and trajectory

```{r}
#| eval: false
geopressureviz(tag)
```
