---
title: Download wind
editor: source
description: https://raphaelnussbaumer.com/GeoPressureManual/geopressuretemplate-wind.html
---

This script will help you download the wind data for a `tag` and define the movement model.


```{r setup}
id <- "34KB"

knitr::opts_knit$set(root.dir = here::here())
library(GeoPressureR)
```



## Create tag

Make sure you have already created the label file with the "1-label.qmd" script.

```{r, cache = TRUE, message=FALSE}
tag <- geopressuretemplate_tag(id, quiet = F)
```

## Download wind data

The [job package](https://lindeloev.github.io/job) allows you to download the wind data in the background and let your R console free to use.

```{r, eval = FALSE}

tag_download_wind(tag, workers = 8)

```

Check requests at <https://cds.climate.copernicus.eu/requests>

## Define movement model

::: callout-danger
Make sure to update the type from `"gs"` to `"as"` in `config.yml`:

```yml
graph_set_movement:
  type: "as"
```
:::

### Add wind data

```{r}
graph <- graph_create(
  tag,
  thr_likelihood = config::get("graph_create", id)$thr_likelihood,
  thr_gs = config::get("graph_create", id)$thr_gs
)
```

```{r}
graph <- graph_add_wind(
  graph,
  pressure = tag$pressure,
  thr_as = config::get("graph_add_wind", id)$thr_as
)
```

### Set movement model

Check that the movement model defined in `config.yml` is adequate.

```{r}
graph <- graph_set_movement(
  graph,
  bird = bird_create(config::get("bird_create", id)$scientific_name)
)
```

Check the movement model

```{r}
plot_graph_movement(graph)

path_most_likely <- graph_most_likely(graph, quiet = TRUE)
marginal <- graph_marginal(graph, quiet = TRUE)
path_simulation <- graph_simulation(graph, nj = 10, quiet = TRUE)

plot(marginal, path = path_most_likely)
plot_path(path_simulation, plot_leaflet = FALSE)
```


```{r}

edge_simulation <- path2edge(path_simulation, graph)
edge_most_likely <- path2edge(path_most_likely, graph)
knitr::kable(head(edge_most_likely, 3), digits = 1)

library(ggplot2)
plot_graph_movement(graph) +
  geom_histogram(
    data = data.frame(as = abs(edge_simulation$gs - edge_simulation$ws)),
    aes(x = as, y = after_stat(count) / sum(after_stat(count))),
    color = "black",
    fill = NA,
    bins = 100
  )
```

